A Taxonomy of Twists of Supersymmetric Yang--Mills Theories

### 2020-01-24 paper.tex

We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ as in the previous section.
Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
\]

@@

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\Sect\left(\CC^2, \left((T^*\fg \otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$. 
Moreover, this equivalence is $\MU(2)$-equivariant.
\label{thm:4d4Atwist}
\end{theorem}
\begin{proof}
The 4d $\cN=4$ super Yang--Mills theory viewed as a $\cN=2$ theory is 4d $\cN=2$ Yang--Mills theory with matter valued in $U=T^*\fg$. 
Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. 
From Theorem \ref{thm:4dDonaldsontwist} we obtain the desired result.
\end{proof}
%\vspace{-10pt}
%\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
%\begin{itemize}
% \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
% \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
%\end{itemize}

>>>>

We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
\]

@@

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC_{\rm Dol}, B \fg_{\rm Hod})$. 
Moreover, this equivalence is $\MU(2)$-equivariant.
\label{thm:4d4Atwist}
\end{theorem}
\begin{proof}
The 4d $\cN=4$ super Yang--Mills theory viewed as a $\cN=2$ theory is 4d $\cN=2$ Yang--Mills theory with matter valued in $U=T^*\fg$. 
Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. 
From Theorem \ref{thm:4dDonaldsontwist} we obtain that the twist is $\Sect\left(\CC^2, \left((T^*\fg \otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$ as a $\ZZ$-graded theory.

The twisting homomorphism used in Section \ref{sect:4d_2_holomorphictwist} differs from the twisting homomorphism defined above. 
In particular, this equivalence is not $\U(2)$-equivariant. In the present case the fields decompose in the same fashion as in the proof of Theorem \ref{thm:4d4holomorphictwist} which are precisely the fields of $\map(\CC_{\rm Dol}, B \fg_{\rm Hod})$.
\end{proof}
%\vspace{-10pt}
%\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
%\begin{itemize}
% \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
% \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
%\end{itemize}
